Age-related changes in plant growth and traits

### 2015-08-20 results_accessory_v3_alt_reproInv.Rmd
Tidy up use of remake and functions
fixing variable names

```{r, echo=FALSE,results='hide', message=FALSE,warning=FALSE}
library(remake)
create_bindings()

source("scripts/functions.R")
```

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(1,2), cex=1, omi=c(.6,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
plot(accessory_inv~total_repro_inv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp(species))
abline(0,1)
abline(-0.30103,1)
abline(-1,1)
text(120,350,"all RE to accessory tissues",srt=43)
text(12000,720,"10% RE to accessory tissues",srt=43)
text(5,1.5,"50%",srt=43)

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=14, fig.height=14}
options(scipen=10)
par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.3,0.3), mai=c(.8,1,.3,0.3))
mod <- lm (log(total_weight)~log(total_repro_inv), data=subset(SummaryInd,total_repro_inv>0))
plot(total_repro_inv~total_weight,data=subset(SummaryInd,total_repro_inv>0), log="xy",xlab="", col=col.spp(species), pch=16, ylab="Total reproductive investment (mg)",xlim=c(100,2000000))
words.bottom.right.logxy(mod)

@@

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14,warning=FALSE}
par(mfrow=c(2,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
options(scipen=20)
mod <- lm(asin(sqrt(seedset))~log(total_repro_inv),data=subset(SummaryInd,seedset>0&seedset<1))
plot((total_repro_inv)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species),log="y")
words.bottom.right.logy(mod)

mod <- lm(asin(sqrt(prop_propagule))~log(total_repro_inv),data=subset(SummaryInd,prop_propagule>0))
plot((total_repro_inv)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species),log="y")
words.bottom.right.logy(mod)
legend("topright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")

mod <- lm(log(propagule_per_seed)~log(total_repro_inv),data=subset(SummaryInd,seedset>0&seedset<1))
plot((total_repro_inv)~(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1), log="xy",pch=16,col=col.spp(species))
words.bottom.right.logxy(mod)
```

@@

mod <- lm((prop_maxH)~log((total_repro_inv)),data=subset(SummaryInd,prop_maxH>0&total_repro_inv>0))
plot(total_repro_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&total_repro_inv>0), pch=16,col=col.spp(species),log="y", ylab="total reproductive investment (mg)")
words.bottom.right.logy(mod)

@@

- just looking among plants >3 years old  
```{r, echo=FALSE, message=FALSE, fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(1,.1,.7,.1), mai=c(.5,1.1,.2,0.2)) 
tmp <- SummaryInd %>%
  filter(total_repro_inv!=0&age>3) %>%
  group_by(species) %>%
  summarise_each(funs(mean, se), prop_prepollen_all)

@@

tmp2 <- SummaryInd %>%
  filter(total_repro_inv!=0&age>3) %>%
  group_by(species) %>%
  summarise_each(funs(mean, se), prop_packaging_dispersal)

>>>>

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(1,2), cex=1, omi=c(.6,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
plot(accessory_inv~repro_inv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp(species))
abline(0,1)
abline(-0.30103,1)
abline(-1,1)
text(120,350,"all RE to accessory tissues",srt=43)
text(12000,720,"10% RE to accessory tissues",srt=43)
text(5,1.5,"50%",srt=43)

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=14, fig.height=14}
options(scipen=10)
par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.3,0.3), mai=c(.8,1,.3,0.3))
mod <- lm (log(total_weight)~log(repro_inv), data=subset(SummaryInd,repro_inv>0))
plot(repro_inv~total_weight,data=subset(SummaryInd,repro_inv>0), log="xy",xlab="", col=col.spp(species), pch=16, ylab="Total reproductive investment (mg)",xlim=c(100,2000000))
words.bottom.right.logxy(mod)

@@

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14,warning=FALSE}
par(mfrow=c(2,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
options(scipen=20)
mod <- lm(asin(sqrt(seedset))~log(repro_inv),data=subset(SummaryInd,seedset>0&seedset<1))
plot((repro_inv)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species),log="y")
words.bottom.right.logy(mod)

mod <- lm(asin(sqrt(prop_propagule))~log(repro_inv),data=subset(SummaryInd,prop_propagule>0))
plot((repro_inv)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species),log="y")
words.bottom.right.logy(mod)
legend("topright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")

mod <- lm(log(propagule_per_seed)~log(repro_inv),data=subset(SummaryInd,seedset>0&seedset<1))
plot((repro_inv)~(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1), log="xy",pch=16,col=col.spp(species))
words.bottom.right.logxy(mod)
```

@@

mod <- lm((prop_maxH)~log((repro_inv)),data=subset(SummaryInd,prop_maxH>0&repro_inv>0))
plot(repro_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&repro_inv>0), pch=16,col=col.spp(species),log="y", ylab="total reproductive investment (mg)")
words.bottom.right.logy(mod)

@@

- just looking among plants >3 years old  
```{r, echo=FALSE, message=FALSE, fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(1,.1,.7,.1), mai=c(.5,1.1,.2,0.2)) 
tmp <- SummaryInd %>%
  filter(repro_inv!=0&age>3) %>%
  group_by(species) %>%
  summarise_each(funs(mean, se), prop_prepollen_all)

@@

tmp2 <- SummaryInd %>%
  filter(repro_inv!=0&age>3) %>%
  group_by(species) %>%
  summarise_each(funs(mean, se), prop_packaging_dispersal)
